\documentclass[11pt]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\moderncvstyle{classic}
\moderncvcolor{blue}

\familyname{Rochette}
\firstname{Guillaume}
\title{Engineer in Applied Mathematics}

%\address{63 rue de Lessard}{76100 Rouen, France}
\email{rochette.guillaume@gmail.com}
\mobile{+33 (0)6 04 07 73 95}
\extrainfo{\url{https://github.com/GuillaumeRochette}}

\begin{document}
\maketitle
	\section{Educational Background}
		\cventry{2012-2017}{National Institute of Applied Sciences of Rouen (INSA Rouen)}{Rouen, France}{\newline Diplôme d'ingénieur en Mathématiques Appliquées (Orienté Recherche)}{\newline English equivalent : Msc. in Applied Mathematics and Computer Science (Research Oriented)}{Main themes : 
		\begin{itemize}
			\item Statistics, Machine Learning and Artificial Intelligence.
			\item Scientific and Stochastic Calculus, and Numerical Methods.
			\item Mathematical Programming and Operations Research.
		\end{itemize}
		End of Studies' Project :
		\begin{itemize}
			\item Deep Learning for Natural Language Processing applied to Stock Market.
		\end{itemize}
		}
					
		\cventry{2012}{Lycée Paul Langevin}{Suresnes, France}{\newline Baccalauréat Scientifique section Européenne Allemand mention Bien}{\newline English equivalent : A-Levels in Sciences and German with distinction}{}	
	\section{Work experience}
		\cventry{April-October 2017}{Thales Services}{Toulouse, France}{\newline End-of-course Internship - Prototyping of a Search Engine for Satellite Imagery}{}
		{Creation of Deep Learning models adapted to High Resolution Satellite Imagery :
		\begin{itemize}
			\item Automated Cartography and Building Detection, using Image Segmentation.
			\item Similarity Search between Images using Deep Features.
		\end{itemize}
		(\url{https://github.com/GuillaumeRochette/EarthBrowser})}
		\cventry{June-September 2016}{BNP Paribas Personal Finance}{Levallois-Perret, France}{Speciality Internship - Basel II Equity Calculator}{Joint Venture with Commerz Finanz Group. Study of European Financial Regulation and Basel Accords (I and II), Knowledges in Risk Management and Project Management}{}
		\cventry{June-September 2015}{Université du Québec À Montréal (UQÀM)}{Montréal, Québec, Canada}{\newline Technical Internship in Data Mining \& Association Rules Mining under the supervision of Pr. Petko Valtchev}{\newline Study and implementation of numerous algorithms \& creation of a new algorithm for closed-pattern mining}{}
		\cventry{July 2013}{PSA Peugeot-Citroën}{Poissy, France}{\newline Working on the assembly line for 208/C3/DS3 cars}{\newline Electronics and door systems check}{Working in morning \& afternoon shifts.}
%		\cventry{March 2011}{Volksbank Goettingen}{Göttingen, Niedersachsen, Germany}{\newline Marketing and Web Design Department}{\newline Improvement of German Business \& Finance oriented vocabulary}{Greeting customers,organisation of conferences, basic learning of financial advising.}
%		\cventry{December 2010}{Café Vierkötter}{Rösrath, Nordrhein-Westfalen, Germany}{\newline Bakery and pastry}{\newline Improvement of German everyday-life vocabulary, duration : 2 weeks}{}
	
	\section{Qualifications}
		\subsection{Computer Science}
			%\cvitem{Operating Systems}{UNIX, Linux, Debian, Ubuntu, Windows.}
			\cvitem{Programming Languages}{Python, C, C++, MatLab, R, SAS, SQL, Java, Fortran.}

			\cvitem{Machine Learning Frameworks}{Caffe, TensorFlow, SciKit Learn, CUDA.}
		\subsection{Languages}
			\cventry{English}{Level C1}{}{TOEIC Certificate 960/990}{}{}
			\cventry{German}{Level B2/C1}{}{Graduated Deutsches Sprachdiplom Stufe II (DSD II), issued by Kultusministerkonferenz (KMK) in 2012}{}{}{}
	\section{Other competencies}
		\cventry{Education}{Tutoring}{Maths for first-year students.}{}{}{}
		\cventry{Sport}{Handball}{Regional League}{5 years}{}{}
		\cventry{}{Climbing}{2 years}{}{}{}
\end{document}